---
title: "Emerging Tech Hubs in the US"
author: "Bryce Martinez"
date: "July 31, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

# Overview

The question I am trying to answer is: How do we identify an emerging tech hub? The point of this research is to identify emerging tech hubs in the United States and the statistics why theya re considered that.

## Hypothesis

My hypothesis is that cities that are or will become emerging tech hubs will have similar characteristics to those of Silicon Valley and San Fransisco before the rise in cost of living.

## Methodology

Since most of the data needed is public record, gathering data involved searching through public records from the Bureau of Labor Statistics. The characteristics looked at included low housing costs, low unemployment rate, higher mean salaries in the tech industry when compared to other industries, there are large or major tech companies in the city, and an active venture capital environment.

# Data

Load your data here. Where did it come from? Did you do anything special to it?

```{r load_data}
library(readr)
qcew_area <- read.csv("qcew_area_msa_tech.csv")
```

Validate your data
```{r validate_data}

paste("Number of rows:", nrow(qcew_area))

# Columns
paste(names(meetups), sep=" ")
```

Summary is a quick way to make sure it's what you expect.

What states are there?
```{r}
summary(meetups$state)
```

Anything non-US?
```{r}
summary(meetups$country)
```

Anything non-tech?
```{r}
summary(meetups$category.name)
```

# Analysis

How did you go about exploring your question?

How many meetup groups are in each state?

```{r}
ggplot(meetups, aes(x=state, fill=status)) +
  geom_bar() +
  xlab("State") +
  guides(fill=guide_legend(title="Status"))
```

How many members are in each state?

```{r}
ggplot(meetups, aes(x=state, y=members, fill=is.na(next_event.id))) +
  geom_bar(stat="identity") +
  xlab("State") +
  ylab("Members")
  guides(fill=guide_legend(title="Has Next Event?"))
```

Wow, California has a lot!

```{r}
meetups %>% filter(state=="CA") %>% summarise(sum(members))
```

What is the age of the meetups?

```{r}
# convert from epoch time
meetups <- meetups %>%
  mutate(created_date = as.POSIXct(created/1000, origin="1970-01-01"),
         created_y = format(created_date, "%Y"),
         created_my = format(created_date, "%b-%Y"))
```


```{r}
ggplot(meetups, aes(x=created_y, fill=state)) +
  geom_bar() +
  xlab("Created") +
  ylab("Meetup Groups")
  guides(fill=guide_legend(title="State"))
  
```


```{r}
ggplot(meetups %>% filter(state=="CA"), aes(city, members)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Your TURN!

Make this work with the Meetup data:

Plot a histogram with one variable:

```{r}
ggplot(my_data, aes(x=column_name_for_thing_to_count) +
  geom_bar() +
  xlab("Thing I'm Counting")
```

Group and Summarize something in the dataset:

```{r}
# things per month, creates a summarized version of your dataset

things_per_month_summary <- my_things %>%
  group_by(month, person) %>% # how do you want to group?
  summarise(num_things = n(), # number of rows total
			num_unique_things = n_distinct(things), # number of unique things (doesn't count repeats)
            biggest_thing=max(thing),
			smallest_thing=min(thing),
			average_thing=mean(thing),
			middle_thing=med(thing))

# If you don't want to summarize but want to keep rows intact, you can use "mutate" instead
things_per_month_all <- my_things %>%
  group_by(month, person) %>% # how do you want to group?
  mutate(num_things = n(), # number of rows total in the grouping
			num_unique_things = n_distinct(thing), # number of unique things (doesn't count repeats)
            biggest_thing=max(thing),
			smallest_thing=min(thing),
			average_thing=mean(thing),
			middle_thing=med(thing))
```

Plot a summary using a bar chart:

```{r}
# to use a bar plot with summaries, you need to use the keyword "identity"

ggplot(my_data_summary, aes(x=numbers, y=thing) +
  geom_bar(stat="identity") +
  xlab("Thing I'm Numbering") +
  ylab("Numbers")
	   
# to plot a grouped value, use fill
# use position="dodge" for bars next to each other, 
# position="stack" stacks them on top
ggplot(my_data_summary, aes(x=numbers, y=thing, fill=thing_type) +
  geom_bar(stat="identity", position="stack") +
  xlab("Thing I'm Numbering") +
  ylab("Numbers")

# if your things are in the wrong order you can use reorder()
# a "-" in front means descending, otherwise it's ascending (smallest first)
ggplot(my_data_summary, aes(x=numbers, y=thing, fill=reorder(thing_type, -num_things)) +
  geom_bar(stat="identity", position="stack") +
  xlab("Thing I'm Numbering") +
  ylab("Numbers") 
```


Plot 2 different columns using a line graph:

```{r}
ggplot(data = my_data, aes(x = x_axis_thing) +
  geom_point(aes(y = numerical_value1, color="Thing 1"), group=1) +
  geom_line(aes(y = numerical_value1, color="Thing 1"), group=1) +
  geom_point(aes(y = numerical_value2, color="Thing 2"), group=2) +
  geom_line(aes(y = numerical_value2, color="Thing 2"), group=2) +
  ylab("Numbers") +
  xlab("Thing I'm Numbering")
```


